---
title: Quinn Asena Resume"
author: Quinn Asena
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/custom_resume.css', 'css/styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
knit: pagedown::chrome_print    
---


```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
library(tidyverse)
library(glue)

# ======================================================================
# These variables determine how the the data is loaded and how the exports are
# done.

# Is data stored in google sheets? If no data will be gather from the csvs/
# folder in project
using_googlesheets <- FALSE

# Just the copied URL from the sheet
# positions_sheet_loc <- "https://docs.google.com/spreadsheets/d/14MQICF2F8-vf8CKPF1m4lyGKO6_thG-4aSwat1e2TWc"

# Is this sheet available for anyone to read? If you're using a private sheet
# set this to false and go to gather_data.R and run the data loading manually
# once to cache authentication
# sheet_is_publicly_readable <- TRUE

# Is the goal of this knit to build a document that is exported to PDF? If so
# set this to true to have links turned into footnotes at the end of the
# document
PDF_EXPORT <- FALSE


# A global (gasp) variable that holds all the links that were inserted for
# placement at the end
links <- c()

# ======================================================================
# Now we source two external scripts. One contains functions for building the
# text output and the other loads up our data from either googlesheets or csvs

# Functions for building sections from CSV data
source('parsing_functions.R') 

# Load data for CV/Resume
source('gather_data.R')

# Now we just need to filter down the position data to include less verbose
# categories and only the entries we have designated for the resume
position_data <- position_data %>% 
  filter(in_resume) %>% 
  mutate(
    # Build some custom sections by collapsing others
    section = case_when(
      section %in% c('research_positions', 'teaching_positions', 'work_positions') ~ 'positions', 
      TRUE ~ section
    )
  ) 
```



Aside
================================================================================


Contact {#contact}
--------------------------------------------------------------------------------

```{r}
contact_info %>% 
  glue_data("- <i class='fa fa-{icon}'></i> {contact}")
```


<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

Online Resources {#onlineresources}
--------------------------------------------------------------------------------


- `fisheR`: R package for calculating Fisher's Information on time-series available at [github](https://github.com/UoA-eResearch/fisheR).

- `app` [Population growth](https://quinnasena.shinyapps.io/r_logistic/)

- `app` [Population growth for lecture](https://quinnasena.shinyapps.io/growth_app/)

- `lecture` [slides](https://quinnasena.github.io/growth_lecture/pop_growth.html#1)


<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

References {#references}
--------------------------------------------------------------------------------

Professor George Perry

[george.perry@auckland.ac.nz](george.perry@auckland.ac.nz)
<br>
<br>

Associate Professor Janet M Wilmshurst

[janet.wilmshurst@auckland.ac.nz](janet.wilmshurst@auckland.ac.nz)
<br>
<br>
Additional references available on request

Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made w/ [**pagedown**](https://github.com/rstudio/pagedown). 

Source code: [github.com/nstrayer/cv](https://github.com/nstrayer/cv).




Main
================================================================================

Quinn Asena {#title}
--------------------------------------------------------------------------------

_PhD candidate at the University of Auckland exploring ecosystem change using palaeoecological and modelling techniques. I develop ecological simulations to investigate underlying ecosystem dynamics and the reliability of statistical methods used in ecological analyses. I also get hands-on in the field and the lab._

_Master's researched involved environmental monitoring using sensor networks and robotics._

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('education')
```



Selected Positions {data-icon=book-open}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('positions')
```

<br>
<br>

Articles and Publications {data-icon=chess}
--------------------------------------------------------------------------------
::: aside
__Courses__

_Attended several courses during my PhD to improve my software proficiency and scientific understanding including:_

Software courses:

- \- Software Carpentry
- \- Winter Bootcamp
- \- Research Bazaar


University Papers/Modules:

- \- Environmental Data Analysis
- \- Modelling of Environmental Systems

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

__Skills__

- \- <i class="fab fa-r-project"></i> programming
- \- High performance computing
- \- Microscopy
- \- ITRAX core scanning
- \- Peat core preparation
:::

```{r}
position_data %>% print_section('academic_articles')
```
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>


Packages and apps {data-icon=robot}
--------------------------------------------------------------------------------



```{r}
position_data %>% print_section('packages')

```


Selected Workshops and Conferences {data-icon=book}
--------------------------------------------------------------------------------

::: aside
__George Perry Lab__

Interested in the lab group?
Visit George Perry's lab group: [Spatial Ecology Group](https://spatialecol.com/)


<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

__Hobbies and Interests__

- _Keen musician improving my piano skills_
<br>

- _Rock climber, if I'm not working I'm probably up a mountain. Been teaching rock climbing safety in the university club for two years_
:::

```{r}
position_data %>% print_section('workshops_conferences')
```


Volunteering and other Experience {data-icon=balance-scale}
--------------------------------------------------------------------------------



```{r}
position_data %>% print_section('other')

```








