---
title: Quinn Asena Resume"
author: Quinn Asena
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/custom_resume.css', 'css/styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
# knit: pagedown::chrome_print    
---


```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
library(tidyverse)
library(glue)

# ======================================================================
# These variables determine how the the data is loaded and how the exports are
# done.

# Is data stored in google sheets? If no data will be gather from the csvs/
# folder in project
using_googlesheets <- FALSE

# Just the copied URL from the sheet
# positions_sheet_loc <- "https://docs.google.com/spreadsheets/d/14MQICF2F8-vf8CKPF1m4lyGKO6_thG-4aSwat1e2TWc"

# Is this sheet available for anyone to read? If you're using a private sheet
# set this to false and go to gather_data.R and run the data loading manually
# once to cache authentication
# sheet_is_publicly_readable <- TRUE

# Is the goal of this knit to build a document that is exported to PDF? If so
# set this to true to have links turned into footnotes at the end of the
# document
PDF_EXPORT <- FALSE


# A global (gasp) variable that holds all the links that were inserted for
# placement at the end
links <- c()

# ======================================================================
# Now we source two external scripts. One contains functions for building the
# text output and the other loads up our data from either googlesheets or csvs

# Functions for building sections from CSV data
source('parsing_functions.R') 

# Load data for CV/Resume
source('gather_data.R')

# Now we just need to filter down the position data to include less verbose
# categories and only the entries we have designated for the resume
position_data <- position_data %>% 
  filter(in_resume) %>% 
  mutate(
    # Build some custom sections by collapsing others
    section = case_when(
      section %in% c('research_positions', 'teaching_positions', 'work_positions') ~ 'positions', 
      TRUE ~ section
    )
  ) 
```



Aside
================================================================================


Contact {#contact}
--------------------------------------------------------------------------------

```{r}
contact_info %>% 
  glue_data("- <i class='fa fa-{icon}'></i> {contact}")
```


<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

<!-- Online Resources {#onlineresources} -->
<!-- -------------------------------------------------------------------------------- -->

<!-- - Workshop: [Quarto for Colaboration](https://github.com/QuinnAsena/resbaz2022) -->

<!-- - `fisheR`: R package for calculating Fisher's Information on time-series. Available at [github](https://github.com/UoA-eResearch/fisheR). -->

<!-- - `app:` [Population growth](https://quinnasena.shinyapps.io/r_logistic/) -->

<!-- - `app:` [Population growth for lecture](https://quinnasena.shinyapps.io/growth_app/) -->

<!-- - Lecture: [Ecological modelling](https://quinnasena.github.io/growth_lecture/pop_growth.html#1) -->

<!-- <br> -->
<!-- <br> -->
<!-- <br> -->
<!-- <br> -->
<!-- <br> -->
<!-- <br> -->
<!-- <br> -->

References {#references}
--------------------------------------------------------------------------------

Professor Jack Williams (Postdoc PI)

[jwwilliams1@wisc.edu](jwwilliams1@wisc.edu)
<br>
<br>

Professor George Perry (PhD Supervisor)

[george.perry@auckland.ac.nz](george.perry@auckland.ac.nz)
<br>
<br>

Professor Anthony Ives (Postdoc PI)

[arives@wisc.edu](arives@wisc.edu)

<!-- Associate Professor Janet M Wilmshurst -->

<!-- [janet.wilmshurst@auckland.ac.nz](janet.wilmshurst@auckland.ac.nz) -->
<br>
<br>

<!-- Associate Professor Giovanni Coco -->

<!-- [g.coco@auckland.ac.nz](g.coco@auckland.ac.nz) -->


Citations and h-index
--------------------------------------------------------------------------------

- **Citations: 55**
- **h-index: 3**




Main
================================================================================

Quinn Asena {#title}
--------------------------------------------------------------------------------

_Post-doctoral research associate developing and applying new statistical methods to palaeoecological data to understand ecosystem responses to environmental change. Working with Jack Williams and Tony Ives on data across North America on an NSF funded project: Abrupt Change in Ecosystems. I also like to get hands on in the field and lab._

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('education')
```

Selected Positions {data-icon=book-open}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('positions')
```

Articles and Publications {data-icon=chess}
--------------------------------------------------------------------------------


```{r}
position_data %>% print_section('academic_articles')
```
<br>
<br>



Packages, apps and resources {data-icon=robot}
--------------------------------------------------------------------------------

::: aside
__George Perry Lab__

Interested in the lab group?
Visit George Perry's lab group: [Spatial Ecology Group](https://spatialecol.com/)

<br>
<br>
<br>

__Williams Lab__

Check out the [Williams lab](https://williamspaleolab.github.io/)

<br>
<br>
<br>

__Ives Lab__

See what the [Ives Lab](https://ives.labs.wisc.edu/) group do


:::

```{r}
position_data %>% print_section('packages')

```

<br>

Selected Workshops and Conferences {data-icon=book}
--------------------------------------------------------------------------------

::: aside

__Hobbies and Interests__

- _Keen musician improving my piano skills_
<br>

- _Rock climber, if I'm not working I'm probably up a mountain. I teach rock climbing safety at university clubs._
:::

```{r}
position_data %>% print_section('workshops_conferences')
```









